Verifying Demonstrations

### 2018-05-25 paper/RelatedWork.tex
Removes Seb's comment and dbosk's reply

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
based on a selected space.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
\seb{what are the meaning of the choice of density estimates, it is a way to 
  specify an apriori assumption about the density of the crowd or to choose 
  between a min, average, max estimates?}
\daniel{Yes.}
This is similar to the method usually used by police (\eg for the protests in Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.

>>>>

Among more recent methods, there is an application called CrowdSize~\cite{CrowdSize} that can estimate the size of a crowd 
based on a selected space.
Once the user has specified the zone, he selects one of three pre-set density estimates: light, medium or dense.
This is similar to the method usually used by police (\eg for the protests in 
Seoul):
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{p}olice presume\textins*{d} that, when sitting, six people would 
  fill a space of 
  3.3 square meters
  \textelp{}
  The same area would hold nine or 10 people when standing%
}.
This method is not verifiable unless the user takes a picture of the crowd, in which case it inherits the verifiability properties of the previous method.
